---
title: "tshw3"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("~/Desktop/tshw3")
data1=read.csv("data1.csv")
data2=read.csv("data2.csv")
library("astsa")
```

```{r data1}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem 1,Problem2

time plot of data1.
It seems not stationary ,since the mean level is changing over time. 
```{r}
plot.ts(data1[,2])
```


time plot of data2
It seems not stationary ,since the mean level is changing over time. 
```{r}
plot.ts(data2[,2])
```

## Problem 3

Identify some possible AR(P) Model.

Take difference on data1 and plot it
```{r }
diff.data1=diff(data1[,2])
plot.ts(diff.data1)
```
It seems more stationary.

Since pacf plot significant between 2~5,I choose p=4,5 to bulid the model.
```{r  }
acf2(diff.data1)
```


Take difference on data2 and plot it
```{r  }
diff.data2=diff(data2[,2])
plot.ts(diff.data2)
```
It seems more stationary.

Since pacf plot significant between 2~5,I choose p=4,5,9 to bulid the model.
```{r }
acf2(diff.data2)
```


## Problem 4,5

for data1 ARIMA(4,1,0) model
The residual plot seems stationary.
The acf plot shows the residuals has little serial correlation,but the Ljung Box test shows serial correlations when p=8,9.
```{r  }
model_data1_p4=arima(data1[,2],order = c(4,1,0))
tsdiag(model_data1_p4,gof=12)
```

for data1 ARIMA(5,1,0) model
The residual plot seems stationary.
Both Ljung-Box and  acf plot shows the residuals has little serial correlation.
```{r  }
model_data1_p5=arima(data1[,2],order = c(5,1,0))
tsdiag(model_data1_p5,gof=12)
```

for data2 ARIMA(4,1,0) model
The residual plot seems stationary.
The acf plot shows the residuals has little serial correlation,but the Ljung Box test shows serial correlations when lag larger than 4
```{r  }
model_data2_p4=arima(data2[,2],order = c(4,1,0))
tsdiag(model_data2_p4,gof=12)
```

for data2 ARIMA(5,1,0) model
The residual plot seems stationary.
The acf plot shows the residuals has little serial correlation,but the Ljung Box test shows serial correlations when lag larger than 5
```{r  }
model_data2_p5=arima(data2[,2],order = c(5,1,0))
tsdiag(model_data2_p5,gof=12)
```

for data2 ARIMA(9,1,0) model
The residual plot seems stationary.
Both Ljung-Box and  acf plot shows the residuals has little serial correlation.
```{r  }
model_data2_p9=arima(data2[,2],order = c(9,1,0))
tsdiag(model_data2_p9,gof=12)
```

For data1 we can use the ARIMA(5,1,0) model ,since the residuals of the model is more likely to satisfy the white noise assumption .

For data2 we can use the ARIMA(9,1,0) model ,since the residuals of the model is more likely to satisfy the white noise assumption .

## Problem 6
```{r  }
result1= predict(model_data1_p5,n.ahead = 12)
result1
plot(1:length(data1[,2]),data1[,2],type='l')
points(length(data1[,2]):(length(data1[,2])+11),result1$pred,pch='0',cex=0.2)
```

```{r  }
result2= predict(model_data2_p9,n.ahead = 12)
result2
plot(1:length(data2[,2]),data2[,2],type='l')
points(length(data2[,2]):(length(data2[,2])+11),result2$pred,pch='0',cex=0.2)
```