---
title: "Time Series hw5"
output: pdf_document
---

```{r setup, include=FALSE}
library(tseries)
library(astsa)
series1=read.table("arima1.txt")
series2=read.table("arima2.txt")
rwalk=read.table("randomwalk.txt")
```

1. arima1 
not stationary
```{r series1}
plot.ts(series1$x)
```

D=1 seems stationary.
```{r }
plot.ts(diff(series1$x))
```

seems stationary
```{r }
adf.test(diff(series1$x),alternative="stationary",k=20)
```

the residuals for (p,d,q)=(3,1,3) seems reasonable.
```{r }
acf2(diff(series1$x))
res1=arima(series1$x,c(3,1,3))
tsdiag(res1)
```

2. arima2
not stationary
```{r series2}
plot.ts(series2)
```

D=2 seems stationary.
```{r }
plot.ts(diff(diff(series2$x)))
```

seems stationary
```{r }
adf.test(diff(diff(series2$x)),alternative="stationary",k=20)
```

the residuals for (p,d,q)=(2,2,3) seems reasonable.
```{r }
acf2(diff(series2$x))
res2=arima(series2$x,c(3,1,3))
tsdiag(res2)
```

3. Random walk
```{r rwalk}
plot.ts(rwalk)
```

the residual violate the assumption of white noise
```{r}
time=1:500
tsdiag(arima(rwalk,order=c(0,0,0),xreg=time))
```

can't reject null hypothesis under significance level 0.05.
```{r}
adf.test(rwalk$x,alternative="stationary",k=1)
```

The model fits well,since the residuals seems reasonable.
```{r}
tsdiag(arima(rwalk,order=c(0,1,0),xreg=time))
```